Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-05-23 Latex/sections/acknowledgement.tex

The authors thank the Cylon team (Ignacio Dorado Llamas, Timothy Randolph, Camilo Andres Reyes Mantilla) for designing and building the prototype and Timo Burger for acquiring the floating table data set.
Special thanks to Dieter Ziegler and Sergio Montenegro for supporting our work.
We acknowledge funding from the ESA Contract No. 4000130925/20/NL/GLC for the ``DAEDALUS -- Descent And Exploration in Deep Autonomy of Lava Underground Structures'' Open Space Innovation Platform (OSIP) lunar caves-system study and the Elite Network Bavaria (ENB) for providing funds for the academic program ``Satellite Technology''.

>>>>

The authors thank the Cylon team (Ignacio Dorado Llamas, Timothy Randolph, Camilo Andres Reyes Mantilla) for designing and building the prototype and Timo Burger for acquiring the floating table data set.
Special thanks to Dieter Ziegler and Sergio Montenegro for supporting our work.
We acknowledge funding from the ESA Contract No. 4000130925/20/NL/GLC for the study ``DAEDALUS -- Descent And Exploration in Deep Autonomy of Lava Underground Structures'' within the Open Space Innovation Platform (OSIP) lunar caves-system and the Elite Network Bavaria (ENB) for providing funds for the academic program ``Satellite Technology''.

### 2021-05-23 Latex/sections/simulation.tex

The Livox-Mid100 laser scanner consists of three smaller-sized Mid40 scanners arranged to provide an overall field-of-view of \SI{98.4}{\degree} (Horizontal) by \SI{38.4}{\degree} (Vertical).
It provides a range precision of \SI{2}{\centi\meter} up to \SI{20}{\meter} range and yields \SI[per-mode=symbol]{300,000}{\pts\per\second}.
A particular advantage of the Livox laser scanners is their unique scanning pattern.
The scanners use two motorized, so-called Risley prisms to steer the beam deflectance.
For the specific ratio of rotation speeds used in the Livox scanners, the beam traces out a non-repetitive, flower-shaped scanning pattern~\cite{thorlabs}.
Since the pattern is non-repetitive, the point density increases with integration time, enabling denser measurements.

>>>>

The Livox-Mid100 laser scanner consists of three Mid40 scanners arranged to provide an overall field-of-view of \SI{98.4}{\degree} (horizontal) by \SI{38.4}{\degree} (vertical).
With a range precision of \SI{2}{\centi\meter} up to \SI{20}{\meter} range it provides \SI[per-mode=symbol]{300,000}{\pts\per\second} with a range precision of \SI{2}{\centi\meter} up to \SI{20}{\meter} range.
A particular advantage of the Livox laser scanners is their unique scanning pattern.
The scanners use two motorized, so-called Risley prisms to steer the beam deflectance.
For the specific ratio of rotation speeds used in the Livox scanners, the beam traces out a non-repetitive, flower-shaped scanning pattern~\cite{thorlabs}.
Since the pattern is non-repetitive, the point density increases with integration time, enabling denser measurements.
